Summary Tables

### 2020-03-02 summary_tables_outcomes.Rmd
Fix number of deaths per 100k

>>>>

### # of deaths due to injury per 100,000 people

    for (cs in names(io[[city]]$outcomes$whw)){
      # cs <- 'Baseline'
      # # cs <- "Baseline"
      # city <- 'accra'
      if (length(names(io[[city]]$outcomes$whw$Baseline)) == 2){
      td1 <- round(io[[city]]$outcomes$whw[[cs]]$nov) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")
      td2 <- colSums(round(io[[city]]$outcomes$whw[[cs]]$whw)) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")
      td3 <- left_join(td2, td1, by = 'mode') %>% mutate(count = rowSums(.[2:3], na.rm = T))
      td3[td3$mode == 'pedestrian', ]$mode <- 'walking'

      td4 <- io[[city]]$true_dist %>% filter(stage_mode %in% td3$mode) %>% dplyr::select(stage_mode)

      td4[, 2] <- round(td4[, 2] / sum(io[[city]]$demographic$population) * 100000, 2)

      el <- inner_join(el, td4, by = 'stage_mode')
    }
    print(kable(el, caption = city))
    td <- el
    names(td)[2:ncol(td)] <- paste(names(td)[2:ncol(td)], city, sep = "_")
